Inferring true changes in microbial abundance from taxonomically-biased microbiome measurements

### 2022-01-08 supplemental-figures.Rmd
Add supplemental figures for fungal case study
Add two additional supplemental figures for the fungal case study, for
the analysis of how the commensals respond to infection.

```{r leopold2020host-variation, fig.cap = '(ref:cap-leopold2020host-variation)'}
fs::path(
  'notebook/_posts/2022-01-06-leopold2020host-t1-samples',
  'leopold2020host-t1-samples_files/figure-html5',
  'variation-in-proportions-and-mean-efficiency-1.svg'
  ) %>%
  include_svg
```

@@

>>>>

```{r leopold2020host-variation, fig.cap = '(ref:cap-leopold2020host-variation)'}
fs::path(
  'notebook/_posts/2022-01-08-leopold2020host-case-study',
  'leopold2020host-case-study_files/figure-html5',
  'variation-in-proportions-and-mean-efficiency-1.svg'
  ) %>%
  include_svg
```

@@

```{r leopold2020host-infection-mean-efficiency-dist, fig.cap = '(ref:cap-leopold2020host-infection-mean-efficiency-dist)'}
fs::path(
  'notebook/_posts/2022-01-08-leopold2020host-case-study',
  'leopold2020host-case-study_files/figure-html5',
  'infection-mean-efficiency-dist-1.svg'
  ) %>%
  include_svg
```

(ref:cap-leopold2020host-infection-mean-efficiency-dist) **The mean efficiency tends to increase after infection due to the high proportion of the pathogen.**

```{r leopold2020host-infection-lfc, fig.cap = '(ref:cap-leopold2020host-infection-lfc)'}
fs::path(
  'notebook/_posts/2022-01-08-leopold2020host-case-study',
  'leopold2020host-case-study_files/figure-html5',
  'infection-lfc-estimates-1.svg'
  ) %>%
  include_svg
```

(ref:cap-leopold2020host-infection-lfc) **Bias correction increases the estimated increase in log proportion in response to infection for commensal taxa across all host genotypes.** Shown are the estimated log fold change (LFC) and 95% confidence intervals from simple linear regression of log (base e) proportion against experimental timepoint for commensal taxa. Negative values indicate that the proportion of the taxon decreased on average in response to infection, which we expect due to the increase in pathogen abundance and the sum-to-one constraint. Bias leads to artificially low estimates, as the pathogen drives an increase in mean efficiency. In Western genotypes, several taxa whose proportion is observed to decrease without correction are instead found to remain stable or even increase when bias is corrected.
